---
title: "4.2 data transformation"
output:
  pdf_document: default
  html_document: default
date: '2022-07-04'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries
library(plyr)
library(dplyr)
library(ggplot2)
library(pastecs)
library(readxl)
library("stringr")


#set working directory
setwd("C:/Users/darge/OneDrive/Documents/1. Data Science/DSC 520 - Statistics for Data Science/dsc520")

#data set
housing <- read_excel("data/week-6-housing.xlsx")

```
1. Use the apply function on a variable in your dataset

```{r }
apply(X= housing, MARGIN=2, FUN = max)
```
2. Use the aggregate function on a variable in your dataset

```{r }
# Continuous variable first, then categorical variable
aggregate(sq_ft_lot ~ ctyname, housing, mean)
```

3. Use the plyr function on a variable in your dataset – more specifically, I want to see you split some data, perform a modification to the data, and then bring it back together

```{r}
sq_foot_average <- ddply(housing, summarise, .variables = c("ctyname"), sq_average <- mean(sq_ft_lot,na.rm = T))
sq_foot_average

living_sq_foot_average <- ddply(housing, summarise, .variables = c("ctyname"), living_sq_average <- mean(square_feet_total_living, na.rm = T))
living_sq_foot_average

combined_sq_foot <- bind_cols(sq_foot_average,living_sq_foot_average)

combined_sq_foot

```
4. Check distributions of the data
    sqare foot is positive skewed.  Most of the data resides at the beginning of the distribution

```{r}
ggplot(housing, aes(x = sq_ft_lot) ) + geom_histogram()
```

5. Identify if there are any outliers

Yes outliers do exist in this date for sq_ft_lot.  Some variables exceed 100,000 sqare feet!
```{r}
ggplot(housing, aes(x = sq_ft_lot) ) + geom_boxplot()
```

6. Create at least 2 new variables

```{r}
names(housing)[2] <- 'Sales_Price'
names(housing)[1] <- 'Sales_Date'
housing$Column_1 <- "Test_1"
housing$Column_2 <- "Test_2"
average_sales_price <- mean(housing$Sales_Price)
housing_column_names <- colnames(housing)

housing

```

