---
title: "ACS_Dinkins_Darius"
output:
  pdf_document: default
  html_document: default
  word_document: default
date: '2022-06-23'
---
The American Community Survey in 2014 contains 7 columns of data:
Id: Ordinal
Id2: Ordinal 
PopGroup: Ordinal
Geography: Categorical
POPGROUP.display-label: Categorical
RacesReported:interval variable
HSDegree: interval variable
BachDegree: interval variable
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(qqplotr)

setwd("C:/Users/darge/dsc520")
survey_2014 <- read.csv('acs-14-1yr-s0201.csv')

str(survey_2014)
nrow(survey_2014)
ncol(survey_2014)
summary(survey_2014)
```
3. Create a Histogram of the HSDegree variable using the ggplot2 package
  1. Set a bin size for the Histogram
     Bins determined by sqrt of data points.  Bin Width determined by (max - min) / bins
  2. Include a Title and appropriate X/Y axis labels on your Histogram Plot.
  
```{r histogram, include=FALSE}
ggplot(survey_2014, aes(x=HSDegree)) + xlab('High School Degrees')  + ylab('Frequency') + geom_histogram(bins = 12, binwidth = 2.85)  

```

4. Answer the following questions based on the Histogram produced:
  1. Based on what you see in this histogram, is the data distribution unimodal?  
      Yes, X appears the most in the data set
      
  2. Is it approximately symmetrical? 
     No. a vertical cannot be drawn in such a way that the shape to the left or right are similar.
     
  3. Is it approximately bell-shaped?
     No, it skews toward a negative distribution
     
  4. Is it approximately normal?
     No, it skews toward a negative distribution
     
  5. If not normal, is the distribution skewed? If so, in which direction?
     The data skews toward a negative distribution
     
  6. Include a normal curve to the Histogram that you plotted.
  
```{r } 
  
ggplot(survey_2014, aes(x=HSDegree)) + geom_histogram(bins = 12, binwidth = 2.85) +
  xlab('High School Degrees')  + ylab('Frequency') + geom_histogram(bins = 12, binwidth = 2.85)  +
  geom_density(aes(y = 2.85*..count..))

```
  
  
  7. Explain whether a normal distribution can accurately be used as a model for this data.
      Normal distribution can not be accurately used as a model for this data.  The data skews in negative manner.  The majority of the data points exist toward the max.
      
5. Create a Probability Plot of the HSDegree variable.
```{r, include = false} ggplot(survey_2014)
```{r}
ggplot(survey_2014, aes(sample =HSDegree)) + stat_qq_point() 

```

6. Answer the following questions based on the Probability Plot:
  1. Based on what you see in this probability plot, is the distribution approximately normal? Explain how you know.
   The distribution is not normal.  It does not form a straight line.
  2.If not normal, is the distribution skewed? If so, in which direction? Explain how you know.
    The distribution is skewed to the left.  If you drew a straight line down the middle, the data points will skew towards the left.  

7. Now that you have looked at this data visually for normality, you will now quantify normality with numbers using the stat.desc() function. Include a screen capture of the results produced.
    
```{r}
library(pastecs)
round(stat.desc(survey_2014[,"HSDegree"], basic = FALSE, norm = TRUE), digits = 3)
```
8. In several sentences provide an explanation of the result produced for skew, kurtosis, and z-scores. In addition, explain how a change in the sample size may change your explanation?

Skew:  Negative skew value indicates a majority of the data points on the right.  This indicates that a large portion of the population has HS degrees

Kurtosis: A positive kurtosis indicates a pointy and heavy-tailed distribution.  This indicates that a large portion of the population has degrees.

Z-Scores: Skew = (-1.675 - 87.632) = -89.307 / 5.118 = -17.44

Z-Scores: kurtosis = (4.353 - 87.632) = -83.279 / 5.118 = -16.272

The z scores are less than 1 by a large margin.  This makes since as a large size of the population will produce large statisitical difference within the data.

