---
title: "5.2 Exercise"
output:
  pdf_document: default
  html_document: default
date: '2022-07-06'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries
library(dplyr)
library(readxl)
library(purrr)
library(stringr)

#set working directory
setwd("C:/Users/darge/OneDrive/Documents/1. Data Science/DSC 520 - Statistics for Data Science/dsc520")

#data set
housing <- read_excel("data/week-6-housing.xlsx")

```

1. Using either the same dataset(s) you used in the previous weeks’ exercise or a brand-new dataset of your choosing, perform the following transformations (Remember, anything you learn about the Housing dataset in these two weeks can be used for a later exercise!)
  1. Using the dplyr package, use the 6 different operations to analyze/transform the data - GroupBy, Summarize, Mutate, Filter, Select, and Arrange – Remember this isn’t just modifying data, you are learning about your data also – so play around and start to understand your dataset in more detail
  
  2. Using the purrr package – perform 2 functions on your dataset.  You could use zip_n, keep, discard, compact, etc.
  3. Use the cbind and rbind function on your dataset
  4. Split a string, then concatenate the results back together

```{r }
#1
housing %>% group_by(building_grade) %>% summarise(AvgPrice=mean(`Sale Price`)) %>% arrange(AvgPrice)
filter(housing, sale_reason == '12' )
housing%>% slice(1:5)
housing %>% select(`Sale Price`, sq_ft_lot) %>% mutate(`Sale Price`/sq_ft_lot)

#2
housing %>% select(`Sale Price`) %>%  map_dbl(sum)
housing %>% select(`Sale Price`) %>% map(compact)

#3
housing_2 <- housing
sale_price_test <-housing %>% select(`Sale Price`)
cbind_example <- cbind(housing_2, sale_price_test)
rbind_example <- rbind(housing_2, housing)

#4
paste("Hello", "Darius", sep = "")
paste("Hello", "Darius", sep = " ")

```

## Including Plots

You can also embed plots, for example:

```{r }
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
