---
title: "ACS_Dinkins_Darius"
output: html_document
date: '2022-06-23'
---
The American Community Survey in 2014 contains 7 columns of data:
Id:
Id2:
PopGroup:
POPGROUP.display-label:
RacesReported:
HSDegree:
BachDegree:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

setwd("C:/Users/darge/OneDrive/Documents/1. Data Science/DSC 520 - Statistics for Data Science/dsc520")
survey_2014 <- read.csv('acs-14-1yr-s0201.csv')

str(survey_2014)
nrow(survey_2014)
ncol(survey_2014)
summary(survey_2014)
```
3. Create a Histogram of the HSDegree variable using the ggplot2 package
  1. Set a bin size for the Histogram
     Bins determined by sqrt of data points.  Bin Width determined by (max - min) / bins
  2. Include a Title and appropriate X/Y axis labels on your Histogram Plot.
  
```{r histogram, include=FALSE}
ggplot(survey_2014, aes(x=HSDegree)) + xlab('High School Degrees')  + ylab('Frequency') + geom_histogram(bins = 12, binwidth = 2.85)  

```

4. Answer the following questions based on the Histogram produced:
  1. Based on what you see in this histogram, is the data distribution unimodal?  
      Yes, X appears the most in the data set
      
  2. Is it approximately symmetrical? 
     No. a vertical cannot be drawn in such a way that the shape to the left or right are similar.
     
  3. Is it approximately bell-shaped?
     No, it skews toward a negative distribution
     
  4. Is it approximately normal?
     No, it skews toward a negative distribution
     
  5. If not normal, is the distribution skewed? If so, in which direction?
     The data skews toward a negative distribution
     
  6. Include a normal curve to the Histogram that you plotted.
  
```{r histogram, include=FALSE} 
  
ggplot(survey_2014, aes(x=HSDegree)) + geom_histogram(bins = 12, binwidth = 2.85) +
  xlab('High School Degrees')  + ylab('Frequency') + geom_histogram(bins = 12, binwidth = 2.85)  +
  geom_density(aes(y = 2.85*..count..))

```
  
  
  7. Explain whether a normal distribution can accurately be used as a model for this data.
      Normal distribution can not be accurately used as a model for this data.  The data skews in negative manner.  The       majority of the data points exist toward the max.
      
5. Create a Probability Plot of the HSDegree variable.
```{r, include = false} ggplot(survey_2014)

```

